Local to global N input modelling

### 2025-06-04 manuscript.qmd
Forgot about jekyll's underscore vendetta

filters:
  - acronyms

execute:
  eval: true
  echo: false
  warning: false
  message: false
  cache: true
  freeze: auto

@@

[Need to put the cohort concept (and harvest timing) in here.]{.aside}

@@

## Total nutrients (amount & source)

```{r patchwork map}
worldmap <- ne_countries(scale = "large", returnclass = "sf")

@@

All analysis was conducted in R version `r R.version[['major']]`.`r R.version[['minor']]` "`r R.version[['nickname']]`" [@R_base]. 
Major packages used include terra [@terra], targets [@targets], future [@future], furrr [@furrr], and the tidyverse [@tidyverse].
For a full list of R packages used see the lockfile on [Github](https://www.github.com).
This manuscript was written in Quarto [@quarto] using TinyTex [@tinytex] and the acronyms extension [@acronyms].

>>>>

# filters:
#   - acronyms

execute:
  eval: true
  echo: false
  warning: false
  message: false
  cache: false
  freeze: auto

@@

```{r patchwork map}
#| fig-cap: |
#|   Possibly use a patchwork map to show spatial results?
#| fig-height: 9
#| fig-width: 9.5

worldmap <- ne_countries(scale = "large", returnclass = "sf")

@@

## Total nutrients

@@

All analysis was conducted in R version `r R.version[['major']]`.`r R.version[['minor']]` "`r R.version[['nickname']]`" [@R_base]. 
Major packages used include `terra` [@terra], `targets` [@targets], `future` [@future], `furrr` [@furrr], `renv` [@renv], and the `tidyverse` [@tidyverse].
For a full list of R packages used see the lockfile on [Github](https://www.github.com).
This manuscript was written in Quarto [@quarto] using TinyTex [@tinytex] and the acronyms extension [@acronyms].
